\section{Contributions}
The main goal of this internship was to adapt the mathematical tools used by musicologists to analyse the relation between some given musical objects so that this tools could become an aid to composition. To do this, we have first decomposed the PK-nets' definition into two steps and noticed that one of these two steps could be used to define bricks allowing to construct musical objects : EK-nets.

We then defined a way of defining a type of musical object : the structural constraint. Solving this constraint (i.e. compute the set of EK-nets that complies with it) allows to get a set of EK-nets that are similar in the sense they all satisfy a same constraint. This way, we have been able to define pitch-classes.%, intervals, and chords in general.

Within a type of object, the main purpose was that, from one object, one could generate some similar object following certain rules. That is what the relational constraint is for and can then be a tool to the composer to find new ideas without starting from a completely random material. This way, we have been able to define a generalization of the transposition of any small categories. %, Tonnetz relation between chords

\section{Perspectives}

Some immediate constructions can be done using this paradigm : we can define chords (small categories strongly connected with exactly one anchor), and then get the T/I inner automorphisms as natural transformation. This would add the K-nets to the toolbox of EK-nets. We could use the constraints of EK-nets to find Forte's interval vectors. These applications are what I aimed for when I came to the concept of EK-nets. Finding a solid framework to use EK-nets (i.e. constraints) was though my priority, and I think I have now strong basis to add most of relational music analysis tools in the EK paradigm.

After having defined K-nets (and therefore Tonnetz), the first future work I will be doing is trying to include constraints (as it has already been studied in \cite{talbot2017interactive}) and in particular EK-constraints in a musical project. The aim of this musical project is to perform live a track that has been already composed but with some propositions of the constraint system to change the MIDI harmonic part of the track to the performer. This will be done as part of a memoir I will be doing during the master MIM at Gustave Eiffel University.

Since the definition of relational constraint is very close (identical, if we do not consider size problems), we could find a new generalization of constraint within the category framework by relying for example on the Pierre Talbot thesis \cite{talbot2018spacetime}.

We also have demonstrated the proximity between the concept of EK-net and PK-net. Since EK-nets are sorts of K-nets in category theory, one could imagine that both concepts can be unified. Indeed, the solutions of constraints being sets, we might define structural constraints as functors from $\text{EKN}_\mathcal{C}$ to $\bf Set$ and relational constraints as endofunctors of $Set$. Even though that might be interesting to look toward that direction, I don't believe that we would obtain all the power of PK-nets.\newline
Another approach that I prefer would be to extend EK-nets to a concept we could call PEK-nets where we use the PK-net definition over the category where structural constraints would be objects and relational would be arrows. This would that such a category exists. Those are only leads but they could be interessant to investigate.

To finish, a tool could be developped to solve the relational constraints partially, especially in the case when we use group EK-nets where the solution is only a substraction.